\documentclass[3p,sort&compress,11pt,fleqn,review]{elsarticle}
\bibliographystyle{elsarticle-num-names}
\usepackage{amsmath,amsfonts,amssymb,siunitx,float,subcaption,setspace,booktabs,diagbox,bm,tikz,mathtools,tikz-3dplot,pgfplots,url}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{lineno}
\usetikzlibrary{shapes.geometric}
\pgfplotsset{compat=1.8}
\journal{}
\newcommand*{\mb}[1]{\bm{#1}}
\newcommand*{\mT}{\mathrm{T}}
\newcommand*{\md}[1]{\mathrm{d}#1}
\newcommand*{\eqsref}[1]{Eq.~(\ref{#1})}
\newcommand*{\figref}[1]{Fig.~\ref{#1}}
\newcommand*{\tabref}[1]{Table~\ref{#1}}
\newcommand*{\algoref}[1]{Algorithm~\ref{#1}}
\newcommand*{\secref}[1]{\S~\ref{#1}}
\newcommand*{\diag}[1]{\text{diag}\left(#1\right)}
\newcommand*{\sign}[1]{\text{sign}\left(#1\right)}
\newcommand*{\dev}[1]{\text{dev}\left(#1\right)}
\newcommand*{\tr}[1]{\text{trace}\left(#1\right)}
\newcommand*{\ddfrac}[2]{\dfrac{\md{#1}}{\md{#2}}}
\newcommand*{\pdfrac}[2]{\dfrac{\partial{#1}}{\partial{#2}}}
\newcommand{\bsigma}{\mb{\sigma}}
\newcommand{\bvarepsilon}{\mb{\varepsilon}}
\newcommand{\beeta}{\mb{\eta}}
\newcommand{\bn}{\mb{n}}
\newcommand{\balpha}{\mb{\alpha}}
\newcommand{\bbeta}{\mb{\beta}}
\newcommand{\bgamma}{\mb{\gamma}}
\newcommand{\bq}{\mb{q}}
\newcommand{\bs}{\mb{s}}
\newcommand{\bc}{\mb{c}}
\newcommand{\be}{\mb{e}}
\newcommand{\bv}{\mb{v}}
\DeclarePairedDelimiter\abs{\lvert}{\rvert}
\DeclarePairedDelimiter\norm{\lVert}{\rVert}
\makeatletter
\let\oldabs\abs
\def\abs{\@ifstar{\oldabs}{\oldabs*}}
\let\oldnorm\norm
\def\norm{\@ifstar{\oldnorm}{\oldnorm*}}
\newenvironment{breakablealgorithm}
{\begin{center}
\refstepcounter{algorithm}
\hrule height.8pt depth0pt \kern2pt
\renewcommand{\caption}[2][\relax]{
{\raggedright\textbf{\ALG@name~\thealgorithm} ##2\par}
\ifx\relax##1\relax
\addcontentsline{loa}{algorithm}{\protect\numberline{\thealgorithm}##2}
\else
\addcontentsline{loa}{algorithm}{\protect\numberline{\thealgorithm}##1}
\fi
\kern2pt\hrule\kern2pt
}}{\kern2pt\hrule\relax
\end{center}}
\begin{document}
\linenumbers
\begin{abstract}
\begin{linenumbers}
The concept of generalised plasticity theory provides an appealing approach to developing efficient finite element models which could improve computational performance and allow flexibility in customising plastic response.
In this work, we revisit its application in developing frame elements and reformulate a concentrated plasticity frame element to allow its axial force to interact with its end moments ($N$-$M$ interaction).
The proposed element formulation relies on the physical implication of axial plasticity and updates its definition accordingly.
By which, a single axial plasticity history can participate in plasticity evolution and $N$-$M$ interaction at both ends.
The new formulation also redefines the hardening rules to recover desired hardening behaviour, which is not available in the previous formulation.
In terms of numerical performance, the new formulation removes the potential bifurcation issue when both ends experience identical pure axial plasticity history.
The proposed frame element is a high--performing alternative to simulate zero--length plastic hinge frame members that are frequently used in simulations in seismic engineering.
\end{linenumbers}
\end{abstract}
\begin{keyword}
concentrated plasticity frame element\sep
$N$-$M$ interaction\sep
generalised plasticity theory\sep
hysteresis model
\end{keyword}
\begin{frontmatter}
\title{Reformulation of Concentrated Plasticity Frame Element With $N$-$M$ Interaction and Generalised Plasticity}
\author[add1]{Theodore~L.~Chang\corref{tlc}}\ead{tlcfem@gmail.com}
\author[add2]{Chin-Long~Lee}
\cortext[tlc]{corresponding author}
\address[add1]{IRIS Adlershof, Humboldt-Universität zu Berlin, Berlin, Germany, 12489.}
\address[add2]{Department of Civil and Natural Resources Engineering, University of Canterbury, Christchurch, New Zealand, 8041.}
\end{frontmatter}
\input{SEC/INTRO}
\input{SEC/THEORY}
\input{SEC/EXAMPLE}
\bibliography{BIB}
\end{document}